Computational methods in landscape ecology

### 2024-06-02 Sections/software.qmd
adds new ideas
adds new comments

@@

### R
<!-- Hesselbarth -->
landscapemetrics
geodiv
vectormetrics
bespatial
motif
?GLCMTextures
?rasterdiv
?terra

>>>>

<!--jn: misc-->
<!-- the need for open-source software in landscape ecology -->
<!-- every proposed method should be open-source and available to the community -->

@@

### R
<!-- Hesselbarth -->
landscapemetrics
geodiv
vectormetrics (also: VecLI -- they mention open source in their paper a few times, but the software seems to be closed source -- https://urbancomp.net/archives/vecliv3beta)
bespatial
LandComp
motif
?GLCMTextures
?rasterdiv
?terra
